---
title: "Geographic information"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
   rmarkdown::render(input_file,
     encoding=encoding,
     output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
author: "masa"
date: '2023-01-26'
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## My new slide

Some content

*** 
A slide without a title


## Title

### Bullet point
- item 2
- item 2

### Numbered items
1. point 1
2. point 2


## Formatting

Plain 

*italiciczed*

**Bold**

`for (i %in% : 10)`



## Some code

```{r}
head(mtcars)
```

## codes

```{r, comment="", echo=TRUE, eval=FALSE}
head(mtcars)
```


## Plot

```{r, echo=FALSE, fig.align="center", fig.cap="my figure"}
library(ggplot2)
p <- ggplot(mtcars, aes(x=wt, y=mpg))+geom_point()+
  labs(x="Weight", y= "MPG", title="MPG vs weight")
p
```






## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

