---
title: "Geographic information"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
   rmarkdown::render(input_file,
     encoding=encoding,
     output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
author: "masa"
date: '2023-01-26'
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plotly)
```


## US Geographic Visualization App

### Description
This `shiny` application shows geographic information of US states using `plotly`. 
The user specify the type of geographical information, and the application 
shows the US map with heat map indicating the level of the geographical 
parameter such as population. The user can also specify the color gradient for 
the heat map.


## Geographical parameters

- Population 
- Income
- Illiteracy
- Life expectation
- Murder
- High School Graduation
- Frost
- Area


## Example 1

```{r, echo=FALSE}
    library(plotly)
    state_df <- data.frame(state.x77)
    state_df$state <- state.abb
    param <- "Population"
    state_df$hover <- with(state_df, paste(state, '<br>', param, ":", param))
    borders <- list(color=toRGB("red"))
    gradation <- "Blues"

    map_options <- list(scope='usa', projection = list(type='albers usa'),
                        showlakes=TRUE, lakecolor=toRGB('white'))

    plot_ly(state_df, z=~Population, text=~hover, locations=~state,
            type='choropleth', locationmode='USA-states',
            color=~Population, colors = gradation, marker=list(line=borders)) %>%
      colorbar(title = param) %>%
      layout(title=paste('US ', param, ' in 1975'), geo=map_options)
```



## Example 2

```{r, echo=FALSE}
    library(plotly)
    state_df <- data.frame(state.x77)
    state_df$state <- state.abb
    param <- "Income"
    state_df$hover <- with(state_df, paste(state, '<br>', param, ":", param))
    borders <- list(color=toRGB("red"))
    gradation <- "Greys"

    map_options <- list(scope='usa', projection = list(type='albers usa'),
                        showlakes=TRUE, lakecolor=toRGB('white'))

    plot_ly(state_df, z=~Income, text=~hover, locations=~state,
            type='choropleth', locationmode='USA-states',
            color=~Income, colors = gradation, marker=list(line=borders)) %>%
      colorbar(title = param) %>%
      layout(title=paste('US ', param, ' in 1975'), geo=map_options)
```



